Compositional Certified Resource Bounds

### 2015-04-14 paper/main.tex
minor

This research is based on work supported in part by NSF grants 1319671
and 1065451, and DARPA grants FA8750-10-2-0254 and FA8750-12-2-0293.
Any opinions, findings, and conclusions contained in this document are
those of the authors and do not reflect the views of these agencies.

>>>>

We thank members of the FLINT team at Yale and anonymous referees for
helpful comments and suggestions that improved this paper and the
implemented tools.  This research is based on work supported in part
by NSF grants 1319671 and 1065451, DARPA grants FA8750-10-2-0254 and
FA8750-12-2-0293, and ONR Grant N00014-12-1-0478.  Any opinions,
findings, and conclusions contained in this document are those of the
authors and do not reflect the views of these agencies.
